Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
More about representation in PCC Workshop

@@

>>>>

One option is to embrace the Semantic Web, because it offers several key benefits:

\begin{itemize}

\item Distributed system with universal addresses and standard mature protocols
\item Open extensible ontology system and existing domain ontologies
\item Existing library and tool support and expertise
\item Interoperability with existing systems

\end{itemize}

Even if personal health records or systems do not use the Semantic Web, there are existing
techniques to integrate with their data.

@@

However, it is important that control of data be sufficiently granular so that patients can choose
to sure it with clinicians, and that clinicians can refer to it in their notes in the patient's health
record.
